On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-05-26 paper.tex
paper -> revising 1

The decision about the evaluation flow is determined by the
\emph{scheduling strategy}. Different strategies may have a
significant impact on performance, and may lead to a different
ordering of solutions to the query goal. Arguably, the two most
successful tabling scheduling strategies are \emph{local scheduling}
and \emph{batched scheduling}~\cite{Freire-96}. Local scheduling tries
to complete subgoals as soon as possible. When new answers are found,
they are added to the table space and the evaluation fails. Answers
are only returned when all program clauses for the subgoal at hand
were resolved. Batched scheduling favors forward execution first,
backtracking next, and consuming answers or completion last. It thus
tries to delay the need to move around the search tree by batching the
return of answers to repeated subgoals. When new answers are found for
a particular tabled subgoal, they are added to the table space and the
evaluation continues.

@@

On the other hand, batched scheduling schedules the evaluation of a
program in a depth-first manner. It favors the forward execution first
instead of backtracking, leaving the consumption of answers and
completion for last. It thus tries to delay the need to move around
the search tree by batching the return of answers. When new answers
are found for a particular tabled subgoal, they are added to the table
space and the execution continues. For some situations, this results
in creating dependencies to older subgoals, therefore enlarging the
current CDS and delaying the fix-point that guarantees that all
dependent subgoals in a CDS are completely
evaluated~\cite{Sagonas-98}.

@@

@@

In this work, we have presented the PAC strategy, which is a simple
and novel approach for combining the FS design with batched
scheduling. PAC splits answer representation from answer propagation,
allowing the first to be publicly shared among threads while the
second is private to each thread.

>>>>

The decision about the evaluation flow is determined by the
\emph{scheduling strategy}. Different strategies may have a
significant impact on performance, and may lead to a different
ordering of solutions to the query goal. Arguably, the two most
successful tabling scheduling strategies are \emph{local scheduling}
and \emph{batched scheduling}~\cite{Freire-96}. Local scheduling tries
to complete subgoals as soon as possible. When new answers are found,
they are added to the table space and the evaluation fails. Answers
are only returned when all program clauses for the subgoal at hand
were resolved, i.e. after the complete evaluation of subgoal's search
space. Local scheduling has the advantage of minimizing the size of
clusters of dependent subgoals, however it delays propagation of
answers and requires the complete evaluation of the search
space.

Batched scheduling favors forward execution first, backtracking next,
and consuming answers or completion last. It thus tries to delay the
need to move around the search tree by batching the return of answers
to repeated subgoals. When new answers are found for a particular
tabled subgoal, they are added to the table space and the evaluation
continues. Batched scheduling can be an useful strategy in tabled
logic programs that require an eager propagation of answers and/or do
not require the complete set of answers to be found (partial
evaluation of the search space).

@@

On the other hand, batched scheduling schedules the evaluation of a
program in a depth-first manner. It favors the forward execution first
instead of backtracking, leaving the consumption of answers and
completion for last. It thus tries to delay the need to move around
the search tree by batching the return of answers. When new answers
are found for a particular tabled subgoal, they are added to the table
space and the execution continues. For some situations, this results
in creating dependencies to older subgoals, therefore enlarging the
current CDS and delaying the fix-point that guarantees that all
dependent subgoals in a CDS are completely
evaluated~\cite{Sagonas-98}. Batched scheduling can be an useful
strategy in tabled logic programs that require an eager propagation of
answers and/or do not require the complete set of answers to be found
(partial evaluation of the search space).

@@

\begin{figure}[!ht]
%\vspace{-\intextsep}
\centering
\includegraphics[width=10.5cm]{figures/pcc_key-idea.pdf}
\caption{PAC splits answer propagation and answer representation}
\label{fig_tabtries_pcc_key-idea}
%\vspace{-1.0\intextsep}
\end{figure}

@@

In this work, we have presented the PAC strategy, which is a simple
and novel approach for combining the FS design with batched
scheduling. PAC splits answer representation from answer propagation,
and allows the first to be publicly shared among threads while the
second to be private to each thread.
